SSA based global code motion of identical computations

### 2017-04-16 acmart-pacmpl-template.tex
profit

Moreover, LLVM has a `getelementptr' instruction which computes the address
where a load or a store would happen. It is a scalar computation and gets
hoisted frequently even if the loads/stores would not get hoisted.  In order to
reduce register pressure while hoisting loads, we have restricted hoisting of
address computations away from their corresponding loads and stores when the
loads and stores cannot be moved.  This restriction is only to mitigate the
limitations of LLVM's register allocator and may be lifted in the future, when
the register allocation rematerialization pass has been improved to catch the
regressions.

@@

\section{SSA based global code motion of identical computations}
\label{sec:implementation-details}
% Ranking of instructions from Zadeck
% Liveness analysis from Ramakrishna

>>>>

Moreover, LLVM has a `getelementptr' instruction which computes the address
where a load or a store would happen. It is a scalar computation and gets
hoisted frequently even if the corresponding loads/stores would not get hoisted.
In order to reduce register pressure while hoisting loads, we have restricted
hoisting of address computations away from their corresponding loads and stores
when the loads and stores cannot be moved.  This restriction is only to mitigate
the limitations of LLVM's register allocator and may be lifted in the future,
when the register allocation rematerialization pass has been improved to catch
these regressions.

@@

\section{SSA based global code motion of identical computations}
\label{sec:implementation-details}
% Move this before legality and profitability??
% Ranking of instructions from Zadeck
% Liveness analysis from Ramakrishna
